Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-12 edubots_surveys.Rnw
adds (partial) questions to methodology refs #20

@@

% Antonio - I include here the description of interaction features. Not sure if it is the best place for it. Move wherever it better fits.
% Olia- in the text below, we refer to "communucation tools", we should be consisten with the terms we use. Should we refere to communication tools? Messaging apps? Chat tools? 
Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what  their feelings and preferences are with regard to the use of communication tools with students, and even using bots or chatbots in the classroom.
In addition the survey asked about the most relevant \textit{Interaction media features} for the teachers with respect to the potential tool to use in class. These features are:
\begin{itemize}
\item \textit{Analytics}: the tool allows to extract data about students performance or development during the academic course on the teacher's subject.
\item \textit{Connectivity}: it is possible to link or connect the tool with other applications.
\item \textit{Familiarity}: it is something already known or previously used, so no need to learn something new.
\item \textit{Hidden Phone}: it is possible to use the tool without showing my phone number, normally using an alias or an own account independent from my physical telephone.
\item \textit{Horizontally}: all the actors are at the same level (for instance, teacher and students). There is not a hierarchy.
\item \textit{Official formation}: the university offers some training courses or talks about the tool (mainly for teachers). 
\item \textit{Pluggability}: the tool offers different pluggins to the teacher, so he/she can deploy his/her own implemented modules.
\item \textit{Sustainability}: teacher should not be worried about the tool maintenance.
\item \textit{Unidirectionality}: only the teacher can publish information in the channel, i.e. students are not allowed to ask or answer.
\item \textit{Officiality}: the tool has been granted by the university where the teacher works. This means normally that there is also technical support by university's staff.
\item \textit{Synchronous communication}: the interactions between teacher and students take place in real time, i.e. it is not a delayed communication scheme such as e-mail.
\end{itemize}

>>>>

% Including questions in surveys
The first survey about the use of messaging apps in class include the following questions:

\textit{1. Regarding the use of messaging apps in class, you prefer ...}
\begin{itemize}
\item A chat group with the students in the same course
\item Students self-organize and with the teacher not being part of any chat group
\item A chat group with the all the students and teachers of the School/High-School/Faculty
\item A chat group with all the students and teachers of the same study year
\end{itemize}

\textit{2. Which messaging app platform do you use to communicate with your peers or students?}
\begin{itemize}
\item Whatsapp
\item Telegram
\item LinkedIn
\item Twitter messages
\item Discord
\item Slack
\item Snapchat
\item The platform provided by your own institution
\item None, I do not use any messaging app to communicate with my students
\end{itemize}

\textit{3. Which kind of chatbots (software that automatically respond to questions or commands) could be useful to improve the learning results with your students or help you managing your course?}
\begin{itemize}
\item Agenda bots that e.g. remind students about project deadlines
\item Bots that collect and provide answers to frequent questions
\item Bots that inform students about their grades
\item Bots that help with the class materials (e.g. searching for topics about a concept, or asking about them)
\end{itemize}

\textit{4. The virtualization of teaching due to the COVID pandemic during this year and the previous one, did it mean any change in your viewpoint or use of messaging apps in class?}
\begin{itemize}
\item No, I did use it before and use it now
\item Yes, I started using safer alternatives
\item Yes, I did not use any messaging platform before but I do use it now
\item No, I did not use any messaging platform before or now
\end{itemize}

@@

% Antonio - I include here the description of interaction features. Not sure if it is the best place for it. Move wherever it better fits.
% Olia- in the text below, we refer to "communucation tools", we should be consisten with the terms we use. Should we refere to communication tools? Messaging apps? Chat tools? 
Specifically, this survey asked the teachers, in addition to general information (such as gender, age, experience, etc), what  their feelings and preferences are with regard to the use of communication tools with students, and even using bots or chatbots in the classroom. In addition the survey asked about the most relevant \textit{Interaction media features} for the teachers with respect to the potential tool to use in class.

The specific questions included in this second survey are listed below:

\textit{1. You prefer the interaction with your students to be ...}
\begin{itemize}
\item Synchronous: students and teacher/s in the same space, simultaneously
\item Asynchronous: the student asks at anytime, the teacher responds whenever possible
\end{itemize}

\textit{2. Regarding the interaction with your students, you ...}
\begin{itemize}
\item Prefer it to be done by institutional means/tools: office hours, forum/messages via the virtual campus, institutional email
\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others.
\end{itemize}

\textit{3. Which media features do you value the most for your interaction with your students?}
\begin{itemize}
\item Familiarity with its use i.e. that I do not need to learn a new tool
\item Familiarity i.e. that I do not need to learn a new tool
\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others.
\end{itemize}

%These features are:
%\begin{itemize}
%\item \textit{Analytics}: the tool allows to extract data about students performance or development during the academic course on the teacher's subject.
%\item \textit{Connectivity}: it is possible to link or connect the tool with other applications.
%\item \textit{Familiarity}: it is something already known or previously used, so no need to learn something new.
%\item \textit{Hidden Phone}: it is possible to use the tool without showing my phone number, normally using an alias or an own account independent from my physical telephone.
%\item \textit{Horizontally}: all the actors are at the same level (for instance, teacher and students). There is not a hierarchy.
%\item \textit{Official formation}: the university offers some training courses or talks about the tool (mainly for teachers). 
%\item \textit{Pluggability}: the tool offers different pluggins to the teacher, so he/she can deploy his/her own implemented modules.
%\item \textit{Sustainability}: teacher should not be worried about the tool maintenance.
%\item \textit{Unidirectionality}: only the teacher can publish information in the channel, i.e. students are not allowed to ask or answer.
%\item \textit{Officiality}: the tool has been granted by the university where the teacher works. This means normally that there is also technical support by university's staff.
%\item \textit{Synchronous communication}: the interactions between teacher and students take place in real time, i.e. it is not a delayed communication scheme such as e-mail.
%\end{itemize}
